Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-09-15 tex/scam/paper.tex
minor edits

\documentclass{article}
\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
\usepackage[hscale=0.7,vscale=0.8]{geometry}

\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{authblk}

\usepackage{yhmath}

\bibliographystyle{plainnat}

\title{Variable Selection in Convex Function Estimation}

%\author{
%Min Xu, Minhua Chen, John Lafferty
%}

\author[1]{Min Xu}
\author[2,3]{Minhua Chen}
\author[2,3]{John Lafferty}

\affil[1]{Machine Learning Department, Carnegie Mellon University}
\affil[2]{Department of Statistics, University of Chicago}
\affil[3]{Department of Computer Science, University of Chicago}

% ENVIRONMENTS
\numberwithin{equation}{section}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheoremstyle{remark}{\topsep}{\topsep}%
     {\normalfont}% Body font
     {}           % Indent amount (empty = no indent, \parindent = para indent)
     {\bfseries}  % Thm head font
     {.}          % Punctuation after thm head
     {.5em}       % Space after thm head (\newline = linebreak)
     {\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}% Thm head spec
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]
\newtheorem{example}{Example}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{definition}{Definition}[section]

@@

% min's macros
\mathchardef\mh="2D

% John's macros
\def\X{\mathcal{X}}
\def\comma{\unskip,~}
\def\truep{p^*}
\def\div{\|\,}
\long\def\comment#1{}
\def\reals{{\mathbb R}}
\def\P{{\mathbb P}}
\def\E{{\mathbb E}}
\def\Cov{\mathop{\text{Cov}}}
\def\supp{\mathop{\text{supp}\kern.2ex}}
\def\argmin{\mathop{\text{\rm arg\,min}}}
\def\arginf{\mathop{\text{\rm arg\,inf}}}
\def\argmax{\mathop{\text{\rm arg\,max}}}
\let\tilde\widetilde
\def\csd{${}^*$}
\def\mld{${}^\dag$}
\def\dos{${}^\ddag$}
\def\W{\widetilde Y}
\def\Z{\widetilde X}
\let\hat\widehat
\let\tilde\widetilde
\def\given{{\,|\,}}
\def\ds{\displaystyle}
\def\bs{\backslash}
\def\1{{(1)}}
\def\2{{(2)}}
\def\pn{{(n)}}
\def\ip{{(i)}}
\def\Xbar{\overline{X}}
\def\except{\backslash}
\def\npn{\mathop{\textit{NPN\,}}}
\def\i{{(i)}}
\def\cE{{\mathcal{C}}}
\def\cM{{\mathcal{M}}}
\def\cF{{\mathcal{F}}}
\def\cP{{\mathcal{P}}}
\def\cG{{\mathcal{G}}}
\def\tr{\mathop{\text{tr}}}
\long\def\comment#1{}
\def\ti#1{#1}
\def\titi#1{\textit{#1}}
\def\cram{{\sc cram}}
\def\spam{{\small\sc SpAM}}
\def\diag{\mathop{\rm diag}}
\def\ones{\mathbf{1}}
\def\threebars{\mbox{$|\kern-.25ex|\kern-.25ex|$}}
\def\fatnorm#1{\threebars #1 \threebars}
\def\rank{\mathop{\rm rank}}
\def\S{\mathcal{S}}
\def\H{\mathcal{H}}
\def\K{{K}}
\def\rank{\mathop{\rm rank}}
\def\half{{1/2}}
\def\Y{\mathbb{Y}}
\def\M{\mathbb{M}}
\def\F{\mathbb{F}}
\def\pinv{{-1}}
%\def\ones{\mathds{1}}
%\def\ones{1}
\def\Res{Z}
\def\Proj{P}
\def\cN{{\mathcal N}}
\def\cT{{\mathcal H}}
\def\coloneqq{:=}
\def\mathbf#1{\mbox{\boldmath $#1$}} 
\def\bar#1{\overline{#1}}

\maketitle

\begin{abstract}
We consider the problem of estimating a convex function of several variables from noisy values of the function at a finite sample of input points. 
\end{abstract}
\vskip10pt

% \tableofcontents

\input{introduction}
\input{related_work}
\input{summary}
\input{additive_faithful}
\input{estimation}
\input{optimization}
\input{sparsistency}
\input{experiments}
\input{discussion}

>>>>

\documentclass[12pt,pdftex,aos]{imsart}
%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}

\RequirePackage[OT1]{fontenc}
\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
\RequirePackage{hypernat}
\usepackage[ruled,section]{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{graphicx}
\usepackage[hscale=0.7,vscale=0.8]{geometry}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{yhmath}

\renewcommand{\baselinestretch}{1.1}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

\input{macros}

@@

\begin{frontmatter}
\title{Faithful Variable Screening for\\ High-Dimensional Convex Regression}
\runtitle{Faithful Variable Screening for Convex Regression}

\begin{aug}
\vskip10pt
\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
\comma 
\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
\and
\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
\address{
\begin{tabular}{ccc}
\\[10pt]
Machine Learning Department & Department of Statistics & Department of Statistics\\
Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
& & University of Chicago
\end{tabular}
%\\[20pt]
%\printead{e1,e2,e3}
}
\end{aug}

\input{abstract}
%\tableofcontents
\vskip20pt
\end{frontmatter}

\maketitle
\vskip10pt

%\tableofcontents

\input{introduction}
\input{summary}
\input{additive_faithful}
\input{estimation}
\input{optimization}
\input{sparsistency}
\input{experiments}
\input{discussion}
